Dewlap color variation in \textit{Anolis sagrei} is maintained among habitats within islands of the West Indies

### 2021-04-10 ms/sections/suppfigures.tex
added explained variance of for all islands to the explained variance table

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/brightness.png}
	\caption{PC1 captures brightness across all islands. (A) Correlation between dewlap brightness (as measured by the mean reflectance from 300 to 700nm in wavelength) and PC1 score across the whole archipelago. (B) Correlation between brightness and PC1 for each island. Pearson's correlation coefficients are reported. ***, $P < 0.001$.}
	\label{fig:brightness}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/brightness.png}
	\caption{PC1 captures brightness across all islands. (A) Correlation between dewlap brightness (as measured by the mean reflectance from 300 to 700nm in wavelength) and PC1 score across all islands. (B) Correlation between brightness and within-island PC1, for each island. Pearson's correlation coefficients are reported. ***, $P < 0.001$.}
	\label{fig:brightness}
\end{figure}
